Spearheading future omics analyses using dyngen, a multi-modal simulator of single cells

### 2021-05-21 manuscript/v5/manuscript.tex
update title

\usepackage{hyperref}
\hypersetup{
  pdftitle={dyngen is a multi-modal simulator for spearheading future single-cell omics analyses},
  pdfauthor={Robrecht Cannoodt; Wouter Saelens; Louise Deconinck; Yvan Saeys},
  hidelinks}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage[numbers]{natbib}

\title{dyngen is a multi-modal simulator for spearheading future single-cell omics analyses}
\author{Robrecht Cannoodt\textsuperscript{$\dagger{}$,1,2,3} \and Wouter Saelens\textsuperscript{$\dagger{}$,1,2,4} \and Louise Deconinck\textsuperscript{1,2} \and Yvan Saeys\textsuperscript{1,2,*}}
\date{20 May 2021}

@@

\hypertarget{abstract}{%
	\section{Abstract}\label{abstract}}

@@

\hypertarget{introduction}{%
	\section{Introduction}\label{introduction}}

@@

\hypertarget{results}{%
	\section{Results}\label{results}}

@@

\hypertarget{discussion}{%
	\section{Discussion}\label{discussion}}

@@

\hypertarget{sec:dyngen-methods}{%
	\section{Methods}\label{sec:dyngen-methods}}

@@

\hypertarget{sec:dyngen-modules}{%
	\subsection{Defining the module network}\label{sec:dyngen-modules}}

@@

\hypertarget{sec:dyngen-grn}{%
	\subsection{Generating the gene regulatory
		network}\label{sec:dyngen-grn}}

@@

\hypertarget{sec:dyngen-reactions}{%
	\subsection{Convert gene regulatory network to a set of
		reactions}\label{sec:dyngen-reactions}}

@@

\hypertarget{propensity-of-transcription-when-n1}{%
	\subsubsection{\texorpdfstring{Propensity of transcription when
			\(N=1\)}{Propensity of transcription when N=1}}\label{propensity-of-transcription-when-n1}}

@@

\hypertarget{propensity-of-transcription-when-n2}{%
	\subsubsection{\texorpdfstring{Propensity of transcription when
			\(N=2\)}{Propensity of transcription when N=2}}\label{propensity-of-transcription-when-n2}}

@@

\hypertarget{propensity-of-transcription-for-an-arbitrary-n}{%
	\subsubsection{\texorpdfstring{Propensity of transcription for an
			arbitrary
			\(N\)}{Propensity of transcription for an arbitrary N}}\label{propensity-of-transcription-for-an-arbitrary-n}}

@@

\hypertarget{propensity-of-transcription-for-a-large-n}{%
	\subsubsection{\texorpdfstring{Propensity of transcription for a large
			\(N\)}{Propensity of transcription for a large N}}\label{propensity-of-transcription-for-a-large-n}}

@@

\hypertarget{independence-synergism-and-basal-expression}{%
	\subsubsection{Independence, synergism and basal
		expression}\label{independence-synergism-and-basal-expression}}

@@

\hypertarget{sec:dyngen-simcell}{%
	\subsection{Simulate single cells}\label{sec:dyngen-simcell}}

@@

\hypertarget{sec:dyngen-experiment}{%
	\subsection{Simulate experiment}\label{sec:dyngen-experiment}}

@@

\hypertarget{sample-cells}{%
	\subsubsection{Sample cells}\label{sample-cells}}

@@

\hypertarget{sample-molecules}{%
	\subsubsection{Sample molecules}\label{sample-molecules}}

@@

\hypertarget{comparison-between-a-dyngen-and-a-reference-dataset}{%
	\subsubsection{Comparison between a dyngen and a reference
		dataset}\label{comparison-between-a-dyngen-and-a-reference-dataset}}

@@

\hypertarget{sec:dyngen-batcheffect}{%
	\subsection{Simulating batch effects}\label{sec:dyngen-batcheffect}}

@@

\hypertarget{sec:dyngen-groundtruth}{%
	\subsection{Determining the ground-truth
		trajectory}\label{sec:dyngen-groundtruth}}

@@

\hypertarget{sec:dyngen-extractgrn}{%
	\subsection{Determining the cell-specific ground-truth regulatory
		network}\label{sec:dyngen-extractgrn}}

@@

\hypertarget{sec:dyngen-nicompare}{%
	\subsection{Comparison of cell-specific network inference
		methods}\label{sec:dyngen-nicompare}}

@@

\hypertarget{sec:dyngen-velcompare}{%
	\subsection{Comparison of RNA velocity
		methods}\label{sec:dyngen-velcompare}}

@@

\hypertarget{sec:dyngen-tacompare}{%
	\subsection{Comparison of trajectory
		alignment}\label{sec:dyngen-tacompare}}

@@

\hypertarget{comparison-of-scalability-and-runtime}{%
	\subsection{Comparison of scalability and
		runtime}\label{comparison-of-scalability-and-runtime}}

@@

\hypertarget{data-availability}{%
	\section{Data Availability}\label{data-availability}}

@@

\hypertarget{code-availability}{%
	\section{Code Availability}\label{code-availability}}

@@

\hypertarget{acknowledgements}{%
	\section{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{author-contributions}{%
	\section{Author contributions}\label{author-contributions}}

@@

\hypertarget{competing-interests}{%
	\section{Competing interests}\label{competing-interests}}

>>>>

\usepackage{hyperref}
\hypersetup{
  pdftitle={Spearheading future omics analyses using dyngen, a multi-modal simulator of single cells},
  pdfauthor={Robrecht Cannoodt; Wouter Saelens; Louise Deconinck; Yvan Saeys},
  hidelinks}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage[numbers]{natbib}

\title{Spearheading future omics analyses using dyngen, a multi-modal simulator of single cells}
\author{Robrecht Cannoodt\textsuperscript{$\dagger{}$,1,2,3} \and Wouter Saelens\textsuperscript{$\dagger{}$,1,2,4} \and Louise Deconinck\textsuperscript{1,2} \and Yvan Saeys\textsuperscript{1,2,*}}
\date{20 May 2021}

@@

\hypertarget{abstract}{%
	\section*{Abstract}\label{abstract}}

@@

\hypertarget{introduction}{%
	\section*{Introduction}\label{introduction}}

@@

\hypertarget{results}{%
	\section*{Results}\label{results}}

@@

\hypertarget{discussion}{%
	\section*{Discussion}\label{discussion}}

@@

\hypertarget{sec:dyngen-methods}{%
	\section*{Methods}\label{sec:dyngen-methods}}

@@

\hypertarget{sec:dyngen-modules}{%
	\subsection*{Defining the module network}\label{sec:dyngen-modules}}

@@

\hypertarget{sec:dyngen-grn}{%
	\subsection*{Generating the gene regulatory
		network}\label{sec:dyngen-grn}}

@@

\hypertarget{sec:dyngen-reactions}{%
	\subsection*{Convert gene regulatory network to a set of
		reactions}\label{sec:dyngen-reactions}}

@@

\hypertarget{propensity-of-transcription-when-n1}{%
	\subsubsection*{\texorpdfstring{Propensity of transcription when
			\(N=1\)}{Propensity of transcription when N=1}}\label{propensity-of-transcription-when-n1}}

@@

\hypertarget{propensity-of-transcription-when-n2}{%
	\subsubsection*{\texorpdfstring{Propensity of transcription when
			\(N=2\)}{Propensity of transcription when N=2}}\label{propensity-of-transcription-when-n2}}

@@

\hypertarget{propensity-of-transcription-for-an-arbitrary-n}{%
	\subsubsection*{\texorpdfstring{Propensity of transcription for an
			arbitrary
			\(N\)}{Propensity of transcription for an arbitrary N}}\label{propensity-of-transcription-for-an-arbitrary-n}}

@@

\hypertarget{propensity-of-transcription-for-a-large-n}{%
	\subsubsection*{\texorpdfstring{Propensity of transcription for a large
			\(N\)}{Propensity of transcription for a large N}}\label{propensity-of-transcription-for-a-large-n}}

@@

\hypertarget{independence-synergism-and-basal-expression}{%
	\subsubsection*{Independence, synergism and basal
		expression}\label{independence-synergism-and-basal-expression}}

@@

\hypertarget{sec:dyngen-simcell}{%
	\subsection*{Simulate single cells}\label{sec:dyngen-simcell}}

@@

\hypertarget{sec:dyngen-experiment}{%
	\subsection*{Simulate experiment}\label{sec:dyngen-experiment}}

@@

\hypertarget{sample-cells}{%
	\subsubsection*{Sample cells}\label{sample-cells}}

@@

\hypertarget{sample-molecules}{%
	\subsubsection*{Sample molecules}\label{sample-molecules}}

@@

\hypertarget{comparison-between-a-dyngen-and-a-reference-dataset}{%
	\subsubsection*{Comparison between a dyngen and a reference
		dataset}\label{comparison-between-a-dyngen-and-a-reference-dataset}}

@@

\hypertarget{sec:dyngen-batcheffect}{%
	\subsection*{Simulating batch effects}\label{sec:dyngen-batcheffect}}

@@

\hypertarget{sec:dyngen-groundtruth}{%
	\subsection*{Determining the ground-truth
		trajectory}\label{sec:dyngen-groundtruth}}

@@

\hypertarget{sec:dyngen-extractgrn}{%
	\subsection*{Determining the cell-specific ground-truth regulatory
		network}\label{sec:dyngen-extractgrn}}

@@

\hypertarget{sec:dyngen-nicompare}{%
	\subsection*{Comparison of cell-specific network inference
		methods}\label{sec:dyngen-nicompare}}

@@

\hypertarget{sec:dyngen-velcompare}{%
	\subsection*{Comparison of RNA velocity
		methods}\label{sec:dyngen-velcompare}}

@@

\hypertarget{sec:dyngen-tacompare}{%
	\subsection*{Comparison of trajectory
		alignment}\label{sec:dyngen-tacompare}}

@@

\hypertarget{comparison-of-scalability-and-runtime}{%
	\subsection*{Comparison of scalability and
		runtime}\label{comparison-of-scalability-and-runtime}}

@@

\hypertarget{data-availability}{%
	\section*{Data Availability}\label{data-availability}}

@@

\hypertarget{code-availability}{%
	\section*{Code Availability}\label{code-availability}}

@@

\hypertarget{acknowledgements}{%
	\section*{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{author-contributions}{%
	\section*{Author contributions}\label{author-contributions}}

@@

\hypertarget{competing-interests}{%
	\section*{Competing interests}\label{competing-interests}}
